Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-07-06 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020_rev2.tex
VSTTE rebuttal

However, the industry demands the \textcolor{blue}{design solution to be the optimum, considering equipment manufacturers and models available on the market and not just minimum or maximum values of current or power for the optimized items. It is necessary to evaluate the electrical compatibility among the equipment as well. This evaluation can only be achieved with specialized PV optimization software. Therefore, the optimal solution is the lowest cost from a list of equipment that meets the electrical demands of a house. It is based on Life Cycle Cost (LCC) analysis \textcolor{red}{add citation}, where the acquisition and replacement cost are considered over a specific period in years.}

@@

\textcolor{blue}{In this paper, which audience is targeted to be from the software verification area, we decided to use a higher-level explanation about the PV sizing. The sizing process involves a set of eighteen equations related to the electrical engineering area, which is detailed online \textcolor{red}{I was unable to open this file}\footnote{\url{https://drive.google.com/file/d/1C\_OEo06Or0TrcaysHtYQAP1awa9VNR-T/view?usp=sharing}}. The flowchart pictured in Fig.~\ref{fig:flow} is the overview of the steps that must be taken to size a stand-alone PV system.}
%
\begin{figure}[h]
\fbox{\includegraphics[width=0.9\textwidth]{flowchart}}
\centering
\caption{\textcolor{blue}{High level description of stand-alone PV system sizing process.}}
\label{fig:flow} 
\end{figure}

@@

Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries, and inverters (line $5$). This procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combines them to assemble a viable (candidate) PV solution, which meets user requirements. A list of forty equipment from ten different manufacturers was provided (as INPUT) to our synthesis engine to allow the choice of every item of PV sizing. Datasheet from each item was necessary to collect technical information. Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars. All this data is available online \textcolor{red}{I was unable to open this file}\footnote{\url{https://drive.google.com/file/d/1DUtM3Ui\_pU54DmtTXnW1DUcanOcXBVeg/view?usp=sharing}}.

@@

If our algorithm does not find a feasible solution among the item of equipment that was provided for our {\sc Synthesize} phase, then the result is unsatisfiable (\textit{UNSAT}). In particular, the program finishes without finding a solution, indicating that it was unable to combine the specific items of equipment to create a feasible solution. 
%
The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution for the constraints and user requirements. The problem for the {\sc Verify} phase is to find the lowest acquisition cost from a list of equipment and components provided by the {\sc Synthesize} phase. 
%
Note that the process described here is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the solution is sound.
The verification engines transform the Algorithm~\ref{alg:opt-algorithm} into the Boolean expressions that are passed to the solver to verify ($C \wedge \neg P$), as described online\footnote{\url{https://drive.google.com/file/d/1Q_hlgUt6AWrNeOtxhFlIpW4P4OPrPyIA/view?usp=sharing}}.

>>>>

However, the industry demands the \textcolor{blue}{design solution to be the optimum, considering equipment manufacturers and models available on the market and not just minimum or maximum values of current or power for the optimized items. It is necessary to evaluate the electrical compatibility among the equipment as well. This evaluation can only be achieved with specialized PV optimization software. Therefore, the optimal solution is the lowest cost from a list of equipment that meets the electrical demands of a house. It is based on Life Cycle Cost (LCC) analysis~\cite{Alsadi2018}, where the acquisition and replacement cost are considered over a specific period in years.}

@@

\textcolor{blue}{In this paper, which audience is targeted to be from the software verification area, we decided to use a higher-level explanation about the PV sizing. The sizing process involves a set of eighteen equations related to the electrical engineering area, which is detailed online \textcolor{red}{I was unable to open this file}\footnote{\url{https://tinyurl.com/yck7dfxt}}. The flowchart pictured in Fig.~\ref{fig:flow} is the overview of the steps that must be taken to size a stand-alone PV system.}
%
\begin{figure}[h]
\fbox{\includegraphics[width=0.9\textwidth]{flowchart}}
\centering
\caption{\textcolor{blue}{High level description of stand-alone PV system sizing process.}}
\label{fig:flow} 
\end{figure}

@@

Our synthesis algorithm uses non-deterministic variables to choose one specific constant from a given list of PV panels, controllers, batteries, and inverters (line $5$). This procedure ensures that our synthesis engine checks all combinations of items from each equipment, and combines them to assemble a viable (candidate) PV solution, which meets user requirements. A list of forty equipment from ten different manufacturers was provided (as INPUT) to our synthesis engine to allow the choice of every item of PV sizing. Datasheet from each item was necessary to collect technical information. Moreover, the price of each item was obtained from available quotations in the market, and if the currency was not in US dollars, then it was used the exchange rate of the day to convert it to US dollars. All this data is available online \textcolor{red}{I was unable to open this file}\footnote{\url{https://tinyurl.com/ycgbsgkp}}.

@@

If our algorithm does not find a feasible solution among the item of equipment that was provided for our {\sc Synthesize} phase, then the result is unsatisfiable (\textit{UNSAT}). In particular, the program finishes without finding a solution, indicating that it was unable to combine the specific items of equipment to create a feasible solution. 
%
The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution for the constraints and user requirements. The problem for the {\sc Verify} phase is to find the lowest acquisition cost from a list of equipment and components provided by the {\sc Synthesize} phase. 
%
Note that the process described here is completely automated and that validation is performed by our {\sc Verify} phase to ensure that the solution is sound.
The verification engines transform the Algorithm~\ref{alg:opt-algorithm} into the Boolean expressions that are passed to the solver to verify ($C \wedge \neg P$), as described online\footnote{\url{https://tinyurl.com/yajfmavl}}.
